Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/content/introduction.tex
Renamed a subsection.

\subsubsection{Discussion and related work.}
Our work is related to a longstanding economics literature on competition vs. innovation, \eg \cite{Schumpeter-42,barro2004economic,Aghion-QJE05}. While this literature focuses on R\&D costs of innovation, ``reputational costs" thereof seem new and specific to exploration.

>>>>

\subsubsection{Related work.}
Our work is related to a longstanding economics literature on competition vs. innovation, \eg \cite{Schumpeter-42,barro2004economic,Aghion-QJE05}. While this literature focuses on R\&D costs of innovation, ``reputational costs" seem new and specific to exploration.
